Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-12 main.tex
:ambulance: Fix noise variance notation

		\begin{subsection}{Low-Complexity Adaptive Design}
			\begin{subsubsection}{Waveform and Active Beamforming}
				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
				\begin{equation}
					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
				\end{equation}
				where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation and the details are omitted here. On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT. It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
				\begin{equation}
					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{equation}
				where the only design variable $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. $\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subchannels and suppresses the weak ones. The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.

				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively. Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point. In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
				\begin{align}
					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{align}
				That is to say, the suboptimal TS scheme only need to design $\alpha$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
			\end{subsubsection}
		\end{subsection}
	\end{section}

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$. $d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is assumed across transmit antennas and IRS elements. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference. We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$. We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.

		\begin{subsection}{Imperfect CSIT}
			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially when the coherence time is short. Hence, we consider an imperfect CSIT model and denote the estimation of direct and cascaded links at subband $n$ as
			\begin{align}
				\hat{\boldsymbol{h}}_{\mathrm{D},n} &= \boldsymbol{h}_{\mathrm{D},n} + \tilde{\boldsymbol{h}}_{\mathrm{D},n} \\
				\hat{\boldsymbol{V}}_{n} &= \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
			\end{align}
			where $\tilde{\boldsymbol{h}}_{\mathrm{D},n}$ and $\tilde{\boldsymbol{V}}_{n}$ are the corresponding estimation errors, whose entries follow i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{\mathrm{D},n}^2)$ and $\mathcal{CN}(0, \epsilon_{n}^2)$, respectively. Perfect CSIT can be regarded as a special case with $\epsilon_{\mathrm{D},n} = \epsilon_{n} = 0$. % For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
		\end{subsection}

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and quantize each reflection coefficient by $b$ bits.
		\end{subsection}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[Waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}. \textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level while approximately convex for a low noise level. Hence, it can be concluded that TS is preferred at low SNR while PS is preferred at high SNR. This is because in the former case, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization. On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer. The result highlights the benefit of dedicated power waveform and the necessity of joint optimization of waveform and splitting ratio.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[$B=1\,\si{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_1mhz.tex}
				}
			}
			\subfloat[$B=10\,\si{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_10mhz.tex}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

>>>>

		\begin{subsection}{Low-Complexity Adaptive Design}
			\begin{subsubsection}{Waveform and Active Beamforming}
				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
				\begin{equation}
					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
				\end{equation}
				where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation and the details are omitted here. On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT. It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
				\begin{equation}
					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{equation}
				where the only design variable $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. $\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subchannels and suppresses the weak ones. The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.

				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively. Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point. In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
				\begin{align}
					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
				\end{align}
				That is to say, the suboptimal TS scheme only need to design $\alpha$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
			\end{subsubsection}
		\end{subsection}
	\end{section}

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$. $d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is assumed across transmit antennas and IRS elements. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n^2=-40\,\si{\dBm}$ at all subbands as reference. We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$. We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.

		\begin{subsection}{Imperfect CSIT}
			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time. Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
			\begin{equation}
				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
			\end{equation}
			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$. Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$. % For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
		\end{subsection}

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
		\end{subsection}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}. \textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level while approximately convex for a low noise level. Hence, it can be concluded that TS is preferred at low SNR while PS is preferred at high SNR. This is because in the former case, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n^2 \le -40\,\si{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization. On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer. The result highlights the benefit of dedicated power waveform and the necessity of joint optimization of waveform and splitting ratio.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[$B=1\,\si{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_1mhz.tex}
				}
			}
			\subfloat[$B=10\,\si{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_10mhz.tex}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}
